Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-12 paper/main.tex
backing up progress on results section   - finished writing up all early list (order manipulation) results   - finished draft of group-level late list results

these order manipulation results suggest several broad patterns. First, most of
the order manipulations we carried out did \textit{not} reliably affect overall

@@

%%%%%
% - next paragraph: relative strengths of order manipulations (compare order manipulations to *other order manipulations* instead of feature rich)

% - and then, another paragraph: stickiness-- compare results on late lists (order manip vs. feature rich, order manip vs. other order manip).

@@

% figure: clustering effects
\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/fingerprints}

>>>>

these order manipulation results suggest several broad patterns
(Figs.~\ref{fig:recall-dynamics}, \ref{fig:fingerprints}). First, most of the
order manipulations we carried out did \textit{not} reliably affect overall

@@

\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/fingerprints}

The above comparisons between memory performance on early lists in the order
manipulation versus feature rich conditions highlight how sorted lists are
remembered differently from random lists. We also wondered how sorting lists
along each feature dimension influenced memory relative to sorting lists along
the other feature dimensions. Participants trended towards remembering early
lists that were sorted semantically better than lexicographically sorted lists
($t(118) = 1.936, p = 0.055$). Participants also remembered visually sorted
lists better than lexicographically sorted lists ($t(119) = 2.145, p = 0.034$).
However, participants showed no reliable differences in recall performance on
semantically versus visually sorted lists ($t(119) = 0.113, p = 0.910$).
Participants temporally clustered semantically sorted lists more strongly than
either lexicographically ($t(118) = 5.572, p < 0.001$) or visually ($t(119) =
6.215, p < 0.001$) sorted lists, but did not show reliable differences in
temporal clustering on lexicographically versus visually sorted lists ($t(119)
= 0.189, p = 0.850$). Participants also showed reliably more semantic
clustering on semantically sorted lists than lexicographically (category:
$t(118) = 3.492, p = 0.001$, size: $t(118) = 3.972, p < 0.001$) or visually
(category: $t(119) = 2.702, p = 0.008$, size: $t(119) = 4.230, p < 0.001$)
sorted lists; more lexicographic clustering on lexicographically sorted lists
than semantically (length: $t(118) = 3.112, p = 0.002$; first letter: $t(118) =
3.686, p = 0.000$) or visually (length: $t(119) = 3.024, p = 0.003$; first
letter: $t(119) = 2.644, p = 0.009$) sorted lists; and more visual clustering
on visually sorted lists than semantically (color: $t(119) = -2.659, p =
0.009$; location: $t(119) = -4.604, p = 0.000$) or lexicographically (color:
$t(119) = -2.366, p = 0.020$; location: $t(119) = -4.265, p < 0.001$) sorted
lists. In summary, sorting lists by different features appeared to have
slightly different effects on overall memory performance and temporal
clustering, and people tended to cluster their recalls along a given feature
dimension more when the studied lists were (versus were not) sorted along that
dimension.

Beyond affecting how we process and remember \textit{ongoing} experiences, what
is happening to us now can also affect how we process and remember
\textit{future} experiences. Within the framework of our study, we wondered: if
early lists are sorted along different feature dimensions, might this affect
how people remember later (random) lists? In exploring this question, we
considered both group-level effects (i.e., effects that tended to be common
across individuals) and participant-level effects (i.e., effect that were
idiosyncratic across individuals).

At the group level, there seemed to be almost no lingering impact of sorting
early lists on memory for later lists. To simplify the presentation, we report
these null results in aggregate across the three feature groupings. Relative to
memory performance on late feature rich lists, participants' memory performance
in all six order manipulation conditions showed no reliable differences
(semantic: $t(125) = 0.487, p = 0.627$; lexicographic: $t(125) = 0.878, p =
0.382$; visual: $t(126) = 1.437, p = 0.153$). Nor did we observe any reliable
differences in temporal clustering on late lists (relative to late feature rich
lists; semantic: $t(125) = 0.146, p = 0.884$; lexicographic: $t(125) = 0.923, p
= 0.358$; visual: $t(126) = 0.525, p = 0.601$). Aside from a slightly increased
tendency for participants to cluster words by their length on late visual order
manipulation lists (more than late feature rich lists; $t(126) = 2.199, p =
0.030$), we observed no reliable differences in any type of feature clustering
on late order manipulation condition lists versus late feature rich lists
($\|t\|$s $\leq 1.234, p$s $\geq 0.220$).

@@

% figure: clustering effects
